
\section{Tasks sharing and schedule}

%	In this chapter you must tell how the task sharing and communication inside the group worked. You must also tell the real schedule and amount of work done by each group member. You are also encouraged to describe the amount of work of each different part you your project. (planning, implementation of different areas of project, testing and documentation etc.)


%	Think and tell also, if you could have shared tasks better. What went wrong compared to the schedule of your original plan and why.
	
The group communicated via e-mail and weekly meetings. The meetings were convenient for keeping everybody up to date on the latest progress and possible changes to how things were done.

After the plan was presented to the assistant in the beginning of the project, a more detailed schedule was made. Milestones were set up for every week and the work was divided and shared with more detail. By November 17th we wanted to be able to create a picture with just spheres, a week later spheres and some other shapes with lights as well, and then by the 30th all the basic functionalities were to work. A shared document was made on Google Docs that we were supposed to tick off sections in every time we finished something.

In practice the project advanced in a different order and for the most part ahead of time. Very quickly we had pictures with spheres, lights, constructive solid geometry, reflections and translusans. The freely movable camera was finished around the time scheduled, while the file reading function was worked on later than we had thought.

Most of the workload was done by Petter, who handled general things such as creating the header files and the file dependencies, but who also did most of the work in World, Light, Thing, Sphere, CSG... Anni handled the camera and its movements and writing the data out to a file. Hilkka made part of Material, Colour and Vect classes and wrote the first version of the file reading function, which Petter then improved and added error handling to.

Testing of each part was done individually and so well that there were no bigger problems when fitting them together. The testing was not planned in detail in advance, but that didn't cause any problems.

Documentation was done together: each group member wrote more or less the same amount.